Research Cases

### 2025-10-15 Code/R/Research/cases_research.Rmd
More mv cases

# no rates
rates.true <- matrix(c(0, 0, 0, 0), ncol = P)
rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), ncol = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), ncol = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), ncol = P)
# rates_case <- "_dsr"
# different by time series rates
# rates.true <- matrix(c(-0.01, -0.02, -0.01, -0.02), ncol = P)
# rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), ncol = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(c(0, 0, 0, 0), ncol = P)
# freqs_case <- "_nf"
# different by summands freqs
freqs.true <- matrix(c(0.2, 0.2, 0.22, 0.22), ncol = P)
freqs_case <- "_dsf"
# different by time series freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.2, 0.22), ncol = P)
# freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), ncol = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), ncol = P)
# freqs_case <- "_cdsf"

@@

complex.signal <- TRUE
complex_case <- "_c" # complex
# complex.signal <- FALSE
# complex_case <- "_r" # real

@@

```{r}
R <- 2

@@

@@

```{r}
print_errors(ssa_err)
summarise_errors(ssa_err)
```

```{r}
print_errors(tssa_err)
summarise_errors(tssa_err)
```

>>>>

# no rates
# rates.true <- matrix(c(0, 0, 0, 0), ncol = P)
# rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), ncol = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), ncol = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), ncol = P)
# rates_case <- "_dsr"
# different by time series rates
rates.true <- matrix(c(-0.01, -0.02, -0.01, -0.02), ncol = P)
rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), ncol = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(c(0, 0, 0, 0), ncol = P)
# freqs_case <- "_nf"
# different by summands freqs
# freqs.true <- matrix(c(0.2, 0.2, 0.22, 0.22), ncol = P)
# freqs_case <- "_dsf"
# different by time series freqs
freqs.true <- matrix(c(0.2, 0.22, 0.2, 0.22), ncol = P)
freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), ncol = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), ncol = P)
# freqs_case <- "_cdsf"

@@

@@

```{r}
R <- 500

@@

print_errors_m <- function(err_df) {
  err_df |> mutate(zapped_error = zapsmall(error)) |> group_by(sd) |> arrange(zapped_error, L_mssa, .by_group = TRUE)
}

@@

```{r}
# print_errors(ssa_err)
print_errors_m(ssa_err)
summarise_errors(ssa_err)
```

```{r}
# print_errors(tssa_err)
print_errors_m(tssa_err)
summarise_errors(tssa_err)
```
